\section{Introduction}

The hybrid control system used by CU InSpace requires network communication between nodes. The nodes consist of a
control input box at the ground control station, the pad control system at the rocket's launch pad and a user interface
that can be placed anywhere with connection to the network.

In this set up, the pad control box is considered a server. It provides sensor measurements as well as information
about the control system's state. It is the only source of truth in the system. No other node should be responsible for
storing state information about the control system.

The UI and input control box form clients. This creates a distinction between two types of client nodes:

\begin{enumerate}
    \item A control node, which is able to issue commands to the control system. There should only be one control node in the
          system.
    \item A telemetry node, which consumes telemetry data for either logging or display. There can be as many of these nodes in
          the system as necessary.
\end{enumerate}

These two distinct types of client nodes inform the decision to distinguish two primary message categories: Control
(Section \ref{sec:control}) and Telemetry \ref{sec:telemetry}.

\subsection{Control}

Control messages provide a specification for issuing commands to the control system and receiving a response. These
commands are for actuating valves and servos, as well as for progressing the arming level of the control system.

Control messages issued from the client to the server are replied to with an acknowledgement containing the status of
the request.

\subsection{Telemetry}

Telemetry messages provide a specification for sending information about the control system state. This includes sensor
measurements, the current arming level, actuator states and warning messages.

Telemetry messages are not requested, unlike the control commands. They are sent in a continuous stream from the server
to the client.

\subsection{Notices}

It should be noted that this specification is designed under the assumption that all messages are sent using TCP over a
local network.

All fields are to be assumed as having little-endian byte ordering unless specified otherwise.
